To log or not to log

### 2022-01-28 main.tex

\paragraph{What happens to the WIS / CRPS when you log it?}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/crps log viz.png}
    \caption{Figure from Johannes: How CRPS changes when you log the observation}
    \label{fig:log-crps-viz}
\end{figure}

>>>>

\paragraph{What happens to the WIS / CRPS when you log it?}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/SIM-effect-log-score.png}
    \caption{Weighted interval score for a forecast distribution that is N(1, 0.2) and different observed values. Top: difference in absolute terms. Bottom: difference in relative terms. Interesting panels are top left and bottom right.}. 
    \label{fig:log-crps-viz}
\end{figure}
